%% start of file `resume.tex'.
%% Copyright 2000-2022 Mirko Gatto (miga@iki.fi).
% This work may be distributed and/or modified under the
% conditions of the MIT license. See the LICENSE file.
%
% Derived from `resume.tex' by Evan Roman available from: https://github.com/evrom/resume/resume.tex

\documentclass[12pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\smdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\newcommand*{\cventryskill}[7][.25em]{%
  \cvitem[#1]{#2}{%
    {\bfseries#3}%
    \ifthenelse{\equal{#4}{}}{}{{#4}}%
    \ifthenelse{\equal{#5}{}}{}{ #5}%
    \ifthenelse{\equal{#6}{}}{}{ #6}%
    .\strut%
    \ifx&#7&%
      \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}
     
\newcommand*{\cvproject}[7][.25em]{%
  \cvitem[#1]{#2}{%
    {\bfseries#3}%
    \ifthenelse{\equal{#4}{}}{}{, {\slshape#4}}%
    \ifthenelse{\equal{#5}{}}{}{, #5}%
    \ifthenelse{\equal{#6}{}}{}{, #6}%
    \strut%
    \ifx&#7&%
    \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}

\usepackage{fontawesome5}

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean
% adjust the page margins
\newcommand{\margins}{23mm}
\usepackage{geometry}
\geometry{top=19mm, right=\margins, left=\margins, bottom=\margins}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Mirko}{Gatto}
%\title{} % omitted for public distribution 
%\address{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
%\phone[mobile]{} % omitted for public distribution
\email{miga@iki.fi}
\social[github][github.com/nekoni]{github.com/nekoni}
\social[github][github.com/mlgatto]{github.com/mlgatto}
\social[linkedin][linkedin.com/in/mirko-gatto]{linkedin.com/in/mirko-gatto} 
\begin{document}
\makecvtitle
\vspace*{-14mm}
\section{About Me}{
I’m a software architect with more than 20 years of experience, specialized in cloud computing. I'm a promoter of operational excellence, security and automation. I love to work in diverse and globally distributed teams. I wake in the morning because there are problems to be solved.
}
\section{Relevant Experience}
\cventry{May 2021 Current}{Principal Software Engineer}{Remote, France}{Trimble Solutions Corporation}{}{
I worked in a distributed team building cloud solutions for the Tekla customers. My roles were DevOps engineer, solutions architect and developer. 
\begin{itemize}
\item Created an interoperability layer between the Trimble identity OAuth service and the legacy Tekla desktop applications, built with AWS, Lambda, .NET Core and C\#.
\item Created the {\href{https://www.tekla.com}{https://www.tekla.com}} service infrastructure, built with AWS, CDK, ECS, CloudFront, TypeScript and Docker.
\item Created the common search service embedded in {\href{https://www.tekla.com}{https://www.tekla.com}} and {\href{https://support.tekla.com}{https://support.tekla.com}}, used daily by thousands of Tekla customers to search support articles and marketing material, built with AWS, Lambda, .NET Core, C\#, TypeScript, React and Elasticsearch.
\item Created a generic cross cloud file synchronization solutions, built with AWS, API Gateway, CDK, Lambda, Azure, CDK Terraform, Functions and TypeScript.
\item Worked as solutions architect, designing cloud based solutions for the Structures divisions teams, using AWS and Azure.
\item I was part of the site reliability team rotation, responding to operational and security incidents using PagerDuty.
\item Developed the security scan pipeline for my teams codebase, using WhiteSource, SonarQube, OWASP ZAP, RESTler and SecurityCodeScan.
\item Developed a CI/CD pipeline with AWS CodeBuild, TypeScript, NodeJs and React.
\end{itemize}
}
\cventry{May 2018 May 2021}{Cloud Software Architect}{Remote, France}{Trimble Solutions Corporation}{}{
I worked in a distributed team building cloud solutions for Tekla customers. My roles were DevOps team leader, solutions architect, cybersecurity specialist and developer.
\begin{itemize}
\item Led the Tekla online DevOps team, worked on the roadmap, technology stack definition and KPIs.
\item Created the Tekla online CI/CD, built with AWS, TeamCity, ECS and Docker.
\item Created the {\href{https://support.tekla.com}{https://support.tekla.com}} service infrastructure, built with AWS, CloudFormation, CloudFront, WAF, ECS and Docker.
\item Created a multi-region interoperability layer between the Tekla desktop applications and the license and identity services, built with AWS, Lambda, .NET Core and C\#.
\item Created the Tekla license SDK used by the Tekla desktop applications, built with .NET Framework, SQLite and C\#.
\item Created the common infrastructure for the Tekla online services, built with AWS, CloudFormation, CloudFront, WAF, S3, Slack, Ansible, Python and Lambda.
\item Created a common cookie banner supporting GDPR or CCPA based on the client geo location, built with AWS, CloudFormation, CloudFront, TypeScript and React.
\item Worked as solutions architect, designing AWS based solutions for the Tekla teams.
\item Worked as cybersecurity champion representative for the Structures division and implemented a set of security controls in Tekla online services.
\end{itemize}
}
\cventry{January 2018 March 2018}{Cloud System Developer}{Zurich, Switzerland}{Cloudreach}{}{
I worked in the cloud enablement team, helping customers implementing solutions based on AWS.
\begin{itemize}
\item Developed the {\href{https://blick.ch}{https://blick.ch}} service infrastructure built with AWS, ECS, CloudFormation and Docker.
\end{itemize}
}
\cventry{April 2015 January 2018}{Software Architect}{Espoo, Finland}{Trimble Solutions Corporation}{}{
I worked in a distributed team building cloud solutions for Tekla customers. My roles were DevOps engineer, solutions architect and developer.
\begin{itemize}
\item Created the Tekla online services AWS infrastructure using CloudFormation, ElasticBeanstalk, Sumologic, DataDog and PowerShell.
\item Designed the migration of 12 Tekla online services to AWS. The services were based on .NET, Java, NodeJs and Drupal.
\item Created a web client application embedded in the Tekla desktop products, built with TypeScript, React, CefSharp, C\# and WPF.
\item Created a tracking and notification service used to collect and process millions of events gathered daily from web, desktop and mobile applications, built with AWS, Lambda, DynamoDB, C\#, .NET Core, TypeScript and React. Created an SDK for occasionally connected clients, built with C\# and SQLite.
\item Created a Java application to perform the migration of hundreds of thousands of Tekla customers accounts to the Trimble common identity.
\item Developed new features in the interoperability layer between Tekla Structures and the Tekla online services, built with C++, C\# .NET and WPF.
\end{itemize}
}
\cventry{January 2011 April 2015}{Software Engineer}{Espoo, Finland}{Tekla Corporation}{}{
I worked in teams building Tekla desktop and web products. My roles were team leader and developer. 
\begin{itemize}
\item Developed an SDK to build desktop and mobile applications, using WPF, Xamarin and C\#. Created technical documentation and trained colleagues.
\item Developed BIM data platform, using ASP.NET, C\#, MongoDB and ODATA. Led the team during the last phase of the project.
\item Developed Tekla BIMsight, a BIM collaboration application, using WPF and C\#.
\item Led the team extending the Construction Management Add-Ons for Tekla Structures.
\item Developed the filtering API and parser for Tekla Structures Open API using C\#.
\end{itemize}
}
\cventry{June 2006 Dec. 2010}{Software Engineer}{Genoa, Italy}{Ansaldo Sistemi Industriali}{}{
I worked as a developer in the R\&D team building the Ansaldo Micro System Environment (AMS), used as controller system in industrial automation.
\begin{itemize}
\item Created a web based diagnostic system built with ASP .NET Framework and C\#.
\item Created a plug-in based application used to provide the infrastructure for configuration, development, deployment and diagnostic of the AMS, built with .NET Framework, Winforms, C\# and MS SQLServer.
\item Trained technical support engineers and automation engineers (Italian/English).
\item Administered a VMWare ESX cluster.
\end{itemize}
}
\cventry{January 2002 June 2006}{Software Engineer}{Genoa, Italy}{Elsag S.p.A.}{}{
I worked as a developer in teams building a automatic fare collection systems and an electricity stock exchange platform.
\begin{itemize}
\item Created a GUI to control ticketing printers, built with Visual C++.
\item Created the coding writer for magnetic tickets and cards, built with C++.
\item Developed a proof of concept version of the new electricity stock exchange platform using ASP.NET 2.0 and JavaScript.
\item Developed a centralized address book service used in the GME websites, built with ASP.NET 2.0 and JavaScript.
\item Developed a data warehouse service used to archive GME market results, built with .NET 1.1 and JavaScript.
\end{itemize}
}
\cventry{January 2000 January 2002}{Junior Software Engineer}{Genoa, Italy}{Telema S.r.l.}{}{
I worked as a junior developer in teams building industrial automation solutions.
\begin{itemize}
\item Created a web application to track employees hours, built with ASP and SQL Server.
\item Developed a desktop software used to control the plastic roll cut, built with C++.
\item Developed a communication module between remotely operated submarine and the tracking system SCADA, built with C++.
\end{itemize}
}
\section{Education, Certifications and Courses}
\cventry{Feb. 2022}{Course}{Microsoft learning}{Azure/AI/DevOps/GitHub}{}{}
\cventry{Dec. 2021}{Course}{MOOC}{DevOps with Kubernetes}{\href{https://devopswithkubernetes.com}{https://devopswithkubernetes.com}}{}
\cventry{Dec. 2020}{Course}{MOOC}{Full Stack Open}{\href{https://fullstackopen.com}{https://fullstackopen.com}}{}
\cventry{July 2020}{Certification}{Azure Fundamentals}{Score 94\%}{}{}
\cventry{Feb. 2018}{Certification}{AWS Solution Architect Associate}{Score 100\%}{}{}
\cventry{March 2017}{Course}{MOOC}{Cybersecurity Base}{\href{https://cybersecuritybase.mooc.fi}{https://cybersecuritybase.mooc.fi}}{}
\cventry{Nov. 2013}{Certification}{Scrum Alliance}{Espoo, Finland}{Scrum Master}{}
\cventry{1999 2000}{Diploma}{Santi Institute}{Genoa, Italy}{C++ Programmer}{}
\cventry{1993 1998}{High School Diploma}{ITC Einaudi}{Genoa, Italy}{Accountant and Programmer}{}
\section{Skills}
\cventryskill{}{Programming Languages:}{}{C\#, TypeScript, Python, Bash, PowerShell}{}{}
\cventryskill{}{Frameworks \& Libraries:}{}{React, .NET Framework, AWS SDK, AWS CDK}{}{}
\cventryskill{}{Document Languages:}{}{HTML, Markdown, OpenAPI (swagger)}{}{}
\cventryskill{}{Databases:}{}{SQLite, DynamoDB}{}{}
\cventryskill{}{Deployment Environments:}{}{Docker, Kubernetes, k3s}{}{}
\cventryskill{}{Cloud Environments:}{}{AWS, Azure, CloudFlare}{}{}
\cventryskill{}{Operating Systems:}{}{Windows, Linux}{}{}
\section{Projects and Open Source}
\cvproject{}{Personal Blog}{\href{https://blog.xops.dev}{https://blog.xops.dev}}{}{}{
My personal blog delivered from my home network, built with Hugo, k3s and CloudFlare, running on a Raspberry Pi cluster.
}
\cvproject{}{Chip-8 Emulator}{\href{https://github.com/nekoni/SharpOtto}{https://github.com/nekoni/SharpOtto}}{}{}{
Created a chip-8 emulator using C\#, .NET Core and WPF.
}
\cvproject{}{NekoDrive NFS Client}{\href{https://github.com/nekoni/nekodrive}{https://github.com/nekoni/nekodrive}}{}{}{
Created an NFS client and libraries for Windows.
}
\cvproject{}{Ryujinx Nintendo Switch emulator}{\href{https://github.com/Ryujinx/Ryujinx}{https://github.com/Ryujinx/Ryujinx}}{}{}{
Contributed to the development of a Nintendo Switch emulator written in C\#.
}
\cvproject{}{This Resume}{\href{https://github.com/mlgatto/resume}{https://github.com/mlgatto/resume}}{}{}{
View the source of this resume in {\fontfamily{cmr}\selectfont \LaTeX}.
}
\end{document}